\chapter{Actors of Startup Connect:} % Write your own chapter title
\label{Chapter3}
\lhead{\emph{Startup Connect}} % Write in your chapter title to set the page header
\section{Project Actors:}
The following are the main actors of Startup Connect:
\begin{itemize}
\item Founder : 
The founder is the primary actor on the platform, possessing talent and ideas but lacking investment. They can display their abilities and concepts, and investors can reach out to them. They do not need to have a team. They can build their team by collaborating with others and others can join by seeking permission from the owner who created the program. The founder can connect with investors and mentors and finalize their deals with the investors.
\item Investor : 
An investor is the   for the platform. A community of investors is needed for getting funding for the startups. Investors come to the platform with capital and a desire to find fresh talent and ideas. By utilizing the platform, they can identify suitable individuals and communities to invest in and agree on becoming a shareholder or receiving profits until the entrepreneur repays the investment. The investor with minimum investing is also entertained as crowdfunding is supported.
\item Mentor: 
Mentors are a crucial part of any startup. They can make a difference in the success of startups.
In the early stages, the startup fails due to a lack of advice. The mentor can support startups for free and give paid sessions.
\item User: 
The user can be a founder or Investor but also can join the team of the founder and can be a co-founder. This platform supports community building and equity so this actor is also important for team building.
\end{itemize}
