\chapter{Features :} % Write your own chapter title
\label{Chapter2}
\lhead{\emph{Startup Connect}} % Write in your chapter title to set the page header
\section{Features:}
The following are some features of Startup Connect:
\begin{itemize}
\item The Founder, Mentor, and Investor can make their profile and add the required information.
\item The founder makes his profile and adds the required info about their skills to show to the investors.
\item The Founder can initiate his startup identity at the platform to collect funding.
\item The Founder can have multiple startups.
\item The user can see the ideas of a person and can join them as a team and start their own as well.
\item The Founder of the program has the authority to add someone to the team.
\item The founder can create a pitch deck, which includes a business plan, financial projections, and other relevant details, to attract potential investors.
\item A mentor can give mentorship through a forum for program discussion.
\item Investors can invest in different programs and one program can get many investments that are crowdfunding.
\item An official agreement is placed between investors and the program owners, and the members are the shareholders whose shares are decided by the owner.
\item A messaging feature is available for every user where they can connect privately.
\item The platform offers a comprehensive dashboard that displays all the essential data and metrics about the user's program, funding, investments, and monthly/yearly Revenue of the Startup.
\item The investor can rate and review the program and its team members based on their performance, which can help other investors make informed decisions.
\item The platform provides advanced analytics and reporting features that allow users to analyze and track their program's performance, funding, and investments in real time.
\item The platform provides a feature for automatic payments to investors, based on the agreed terms and conditions of the agreement.
\item The platform offers a feature for the founder to issue equity to investors, which can be tracked in real-time using the dashboard.
\item The platform offers services such as payment gateways, analytics tools, and marketing services to enhance the user experience.
\item The platform provides a notification system that alerts users about any updates, new investments, or messages related to their program or investments.
\item The program owner can conduct surveys and polls to gather feedback from the team members, investors, and other stakeholders to improve the program's overall performance.
\end{itemize}
