% Chapter 1

\chapter{Introduction :} % Write your own chapter title
\label{Chapter1}
\lhead{\emph{Startup Connect}} % Write in your chapter title to set the page header
To Startup businesses, we as a whole realize marketing is fundamental for all startups, yet it is significant for new startups. Except if the individuals are familiar with your startup and what it offers, they presumably won't buy your items.
\\\\
Entrepreneurs are no strangers to the challenges of securing funding. From attending countless events to making the right connections and following up with potential investors, the journey can be daunting. This project aims to simplify the funding process, making it easier for aspiring entrepreneurs to access the resources they need. The platform combines elements of social interaction with investment. Users create an account, showcase their talents and build a community. Investors can then invest in the projects they find interesting, with terms and conditions agreed upon through a signed agreement. Multiple investors can invest in a single project, with the platform fostering communication and collaboration between investors and entrepreneurs.
\\\\
The inspiration behind our final project on database design is the desire to support entrepreneurs who face challenges in accessing resources to develop their talents and ideas. We've observed that while some people are fortunate to have financial resources, others do not have access to such resources and struggle to experiment with their abilities and implement their ideas. Furthermore, some people may not have access to mentorship which will lead them nowhere and their success affect their progress badly.
\\\\
To make things easier, We are thinking of this platform that not only provides funding for budding business founders but also makes it easier for them to interact with other like-minded people and potential collaborators. Through this website, people may advertise their talents, get funding, and get mentorship. Additionally, users can express their opinions on various concepts and draw inspiration from others.  We must not let innovative ideas die because of the lack of capital.
\section{Main Idea:}
The main idea is 90 percent of startups fail in the early stage due to no or less funding. To make things easier for them, we will make the journey smooth and feasible for their funding. Many platforms are available but most of them are region specific and focus on certain phases of investing. Another drawback is they lack to fill the specific requirements of investors and startups. The negotiating facility is not available for investors. Most of these apps are also niche specific which hurdles the way for many startups. A community environment is also not available for the founders and investors in existing apps.
\\\\
The platform provides mentor-ship support to startups, to ensure the guidance and resources they need to succeed. Through this approach, the platform empowers budding founders to access the resources they need to turn their ideas into reality while also promoting collaboration and community building.
\\\\
The project gives a platform to startups to get funding for their business.The major concept of this project is crowdfunding. Anyone can invest in startups even a very little amount. The startup has the responsibility to give back the money or their profit as per need. The startup can approach big investors on the platform and connect with them to make their funding smooth. They can make agreements and manage the equity of their business. Equity is the percentage division of the ownership of a startup. The founder can give shares of the startup to investors and give them monthly profit payments as their need. For collaboration messaging service is also available for the users. The platform is also a house for mentors. They can give free or paid mentorship to budding founders.
\section{Our Goal: }
Building a community of startups and investors can provide valuable networking and support opportunities. Crowdfunding has become a popular way for startups to raise capital and gain exposure. This project offers crowdfunding support. This project allows investors to collaborate and share investment opportunities. Negotiating funding deals can be a complex and challenging process, especially for early-stage startups. 
\\\\
This project will provide access to legal advisors to facilitate negotiations.Effective communication between startups and investors is essential for successful fundraising. Messaging facility will be provided for communication and collaboration. This project will have equity percentage, funding, and preferred shares for handling each phase of the startup progress. This will enable users to customize their funding deals. Data analytics can help startups and investors make informed decisions about their fundraising activities. The report of analytics in this project will help with decisions. Access to industry experts and advisors can be valuable for startups seeking funding and investors looking for promising investment opportunities. The project is also a platform for mentors that will help founders for seeking advice. It will have a well-designed UI that helps the investors to make the requirements and do the paperwork.




